VFTS682: a confirmed dynamical ejection?

### 2018-05-10 VFTS682.tex
newdataset - Lennon-like
removed images

\section{Introduction}
\label{sec:intro}
\todo{go to major star formation immediately}
\todo{sentence 2:debate of isolated or not}
\todo{paragraph 2 about }
How do stars form is one longstanding question in astrophysics
\cite{lada:03, zinnecker:07}. It is particularly difficult for massive stars, because these are intrinsically rare
\citep[e.g.,][]{salpeter:55,kroupa:01, schneider:18}, evolve fast, and
remain enshrouded in their parent cloud during the formation
process. Moreover, observations of young massive stars reveal a
complicated multipliticy structure which requires
explanation \citep[][]{kobulnicky:07,mason:09,sana:11,sana:12,kiminki:12,chini:12,kobulnicky:14,almeida:17,demarco:17}. Understanding massive star formation, possibly as a
function of metallicity, is a key question given the present and upcoming
transient survey \citep[e.g., LSST, BlackGem, LIGO/Virgo O3][]{}\todo{ref} which
will reveal transients associated to massive stars
evolution and death.

@@

\begin{acknowledgements}
  The background image of \Figref{fig:main} is based on observations made with ESO Telescopes at the La Silla Observatory under programme ID 076.C-0888, processed and released by the ESO VOS/ADP group.
  We are grateful to S.~Torres for extremely useful discussions on the
  Gaia DR2 dataset.
\end{acknowledgements}
\end{document}

>>>>

\section{Introduction}
\label{sec:intro}
\todo{go to major star formation immediately}
\todo{sentence 2:debate of isolated or not}
\todo{paragraph 2 about }
How do massive stars form is one longstanding question in astrophysics
\cite{lada:03, zinnecker:07}. This because they are intrinsically rare
\citep[e.g.,][]{salpeter:55,kroupa:01, schneider:18}, evolve fast, and
remain enshrouded in their parent cloud during the formation
process. Moreover, observations of young massive stars reveal a
complicated multipliticy structure which requires
explanation \citep[][]{sana:12,sana:17}. Understanding massive star formation, possibly as a
function of metallicity, is a key question given the present and upcoming
transient survey \citep[e.g., LSST, BlackGem, LIGO/Virgo O3][]{}\todo{ref} which
will reveal transients associated to massive stars
evolution and death.

Two competing classes of models for massive star formation exist, one predicting 
that massive stars can form in relative isolation \todo{ref}, the other that
they always form in cluster and/or associations, and therefore massive
stars should be rarely isolated \todo{ref}.

@@

\begin{acknowledgements}
  The background image of \Figref{fig:main} is based on observations
  made with ESO Telescopes at the La Silla Observatory under programme
  ID 076.C-0888, processed and released by the ESO VOS/ADP group.
  This research made use of APLpy, an open-source plotting package for Python \cite{robitaille:12}.
  We are grateful to S.~Torres for extremely useful discussions on the
  Gaia DR2 dataset.
\end{acknowledgements}
\end{document}
